\clearpage
\chapter*{\textit{ABSTRACT}}
\addcontentsline{toc}{chapter}{ABSTRACT}

\begin{center}
	\begin{singlespace}
		\center
		\large\bfseries\MakeUppercase{\textit{DEVELOPMENT OF RISC-V BASED HARDWARE ACCELERATOR FOR REINFORCEMENT LEARNING}}
		
		\normalfont\normalsize
		
		By\\
		\bfseries{\textit{Muhammad Sulthan Mazaya \hspace{5mm} NIM: 13320028}}
		
		\vspace{5mm}
		\large\bfseries{\textit{(Engineering Physics Study Program)}}
		\vspace{5mm}
	\end{singlespace}
\end{center}


\begin{singlespace}
	\small
	\textit{\acf{RL} is one of the popular frameworks for developing
		autonomous agents. \ac{RL} serves as an alternative modeling solution for problems in
		systems that are too complex to be mathematically or algorithmically modeled. As
		a result, \ac{RL} is widely employed in domains such as robotics and autonomous driver
		agents. However, despite being a suitable alternative for many problems, \ac{RL} is
		often challenging to use due to hardware resource limitations. This is primarily
		because \ac{RL} typically demands significant hardware resources. This can be a
		hindrance when deploying \ac{RL} models on computers with limited resources, such as
		Internet of Things (IoT) devices or edge computing platforms. Therefore, in this
		research, a akselerator perangkat keras design is proposed to reduce the
		computational power required for \ac{RL} algorithm computation. This akselerator
		perangkat keras design will be implemented on a \acl{FPGA}
		with an RISC-V, an open instruction set architecture, architecture in the form of a
		co-processor. The results achieved in this final project consist of hardware and
		software configurations, along with the design of the software and hardware that
		will be implemented.
	}
	
	\textit{Keywords: reinforcement learning, co-processor, field programmable gate array, RISC-V}
\end{singlespace}
\clearpage

\clearpage
